Reanalysis Step 4: Main Effects Outcome Analysis

### 2025-08-28 reanalysis-2-multiple_imputation.qmd
refactor
faithful to og

```{r setup}
#| include: false
source("dependencies.R")
seed <- 2025
setup_analysis(seed = seed)

@@

# ANALYSIS MODE: "test" or "final"
# test = 2 imputations, 2 iterations (fast)
# final = 50 imputations, 20 iterations (slow but thorough)
analysis_mode <- "test"  # Change to "final" for production run

# Set parameters based on mode
if (analysis_mode == "test") {
  n_imputations <- 2
  n_iterations <- 2
} else if (analysis_mode == "final") {
  n_imputations <- 50
  n_iterations <- 20
} else {
  stop("Invalid analysis_mode. Must be 'test' or 'final'")
}
```

>>>>

```{r setup}
#| include: false
source("dependencies.R")
source("functions.R")  # Load formula definitions and helper functions
seed <- 2025
setup_analysis(seed = seed)

@@

# ANALYSIS MODE: "test" or "final"
# test = 2 imputations, 2 iterations (fast)
# final = 30 imputations, 20 iterations (stability achieved ~20)
analysis_mode <- "final"  # Change to "final" for production run

# Set parameters based on mode
if (analysis_mode == "test") {
  n_imputations <- 2
  n_iterations <- 2
} else if (analysis_mode == "final") {
  n_imputations <- 30
  n_iterations <- 20
} else {
  stop("Invalid analysis_mode. Must be 'test' or 'final'")
}
```

### 2025-08-28 reanalysis-3-propensity_scores.qmd
faithful to og

## Define Enhanced Propensity Score Formula

```{r ps-formula}
# Original formula from get_matching_formula()
# Now enhanced to include DR severity

@@

# Get the enhanced formula for reanalysis (includes dr_severity)
ps_formula_enhanced <- get_matching_formula_reanalysis()

@@

**Propensity score formula:**
```{r print-formula}
# Show the formula being used
print(ps_formula_enhanced)

# Set the formula to use for analysis
ps_formula <- ps_formula_enhanced
```

>>>>

## Define Propensity Score Formula

```{r ps-formula}
# Use original formula from get_matching_formula() 
# to maintain consistency with original analysis

@@

# Get the ORIGINAL formula (does NOT include dr_severity)
ps_formula_original <- get_matching_formula()

@@

**Propensity score formula (original, without DR severity):**
```{r print-formula}
# Show the formula being used
print(ps_formula_original)

# Set the formula to use for analysis
ps_formula <- ps_formula_original
```

### 2025-08-28 reanalysis-4-outcome_analysis.qmd
faithful to og

```{r define-formula}
# Get the enhanced formulas for reanalysis from functions.R
reanalysis_formulas <- get_analysis_formulas_reanalysis()

# Use the full formula for main effects analysis
main_effects_formula <- reanalysis_formulas$full
```

@@

# Display key variables
key_vars <- c("ever_lapse_binary", "dr_severityNPDR", "dr_severityPDR")
key_results <- full_results[full_results$Variable %in% key_vars, ]

kable(key_results, 
      caption = "Key variables from pooled model")
```

>>>>

```{r define-formula}
# Get the ORIGINAL formulas from functions.R
# Using original to maintain consistency with submitted analysis
original_formulas <- get_analysis_formulas()

# Use the full formula (without dr_severity)
main_effects_formula <- original_formulas$full
```

@@

# Display key variables
key_vars <- c("ever_lapse_binary")
key_results <- full_results[full_results$Variable %in% key_vars, ]

kable(key_results, 
      caption = "Final results for lapsing from care")
```
